% !TEX root = ../main.tex

\begin{acknowledgements}

Throughout the capstone design project of ``RISC-V SoC Microarchitecture Design and optimization'', we have received a great deal of support and assistance.

We greatly appreciate our instructor, Dr. Weikang Qian from UM-SJTU Joint Institute at Shanghai Jiao Tong University. As the instructor of our project, he listens to our weekly report and gives many constructive suggestions. Besides, he provides much support for us, not only in the technical part, but also in terms of our future career planning, etc. His insightful feedback pushes us to sharpen our thinking and brings our work to a higher level.

We greatly thank Dr. Jigang Wu, Dr. Chengbin Ma, Dr. Peisen Huang, Dr. Gang Zheng, Dr. An Zou and Dr. Mingjian Li from UM-SJTU Joint Institute at Shanghai Jiao Tong University, who are the course instructors of \textit{VE450 Major Design Experience} at Joint Institute. We also greatly thank the whole teaching assistant team of this course. They teach us many concepts of engineering design process and project management, which helps us explore from the engineering problems and needs to the concept selection and final solutions.

In addition, we would like to express our greatest gratitude to our parents. No matter what kind of difficulties we are facing, they are always there, providing firm and unconditional support for us. We would like to thank our friends and schoolmates at Joint Institute for their personal support in our academic endeavours during the past four years.

Thanks to \href{https://github.com/sjtug/SJTUThesis}{\sjtuthesis~Team} for providing the \LaTeX~template for this thesis document.

\end{acknowledgements}
